---
title: "STAT605 - Project Proposal"
author: "Group #10"
date: "`r Sys.Date()`"
css: proposal.css
# output: html_document
output: rmdformats::material
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra)
```

# Project Description

## Problem Statement

+ Providing artist/track popularity analysis to business owners (entertainment label representatives in this case).
+ The analysis could help them market new artists they plan on launching.

## Questions
We are hoping to answer some of these questions through our analysis

__Analysis Questions:__

+ Who is the most popular artist per genre every year? (summary analysis)
+ Top 5 search queries associated with an a track/artist (user input)
+ The top 5 genres of (top 10?) artists on a given year (user input)
+ Is there any correlation between the popularity of an artist and the chances of their songs being included in a playlist for that genre?

__Modeling Questions:__

+ What are the significant factors that influence the popularity of an artist? (Figuring out factors that are statistically significant?)
+ Given a combination of music genres, can we predict the popularity of a track?



# Code to read the data

Our main data set is located [here](https://media.githubusercontent.com/media/NiharikaCNR/STAT605-Project/main/data/main_dataset.csv) on GitHub. It has 26 unique variables as seen below.

```{r, echo=FALSE}
main_data = read_csv("../data/main_dataset.csv")
```

```{r}
glimpse(main_data)
```

# Description of Variables

## main_dataset.csv

```{r, echo=FALSE}
description_of_variables = read_csv("../data/description_of_variables.csv")
kable(description_of_variables, format = "html") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed"))
```

# Statistical Methods
```{r}
```

# Computational Steps

1. Data Pre-processing:
    + Handle any missing values in the data set.
    + Remove any duplicate entries.
2. Exploratory Data Analysis:
    + Descriptive Statistics - Generate summary statistics for key variables.
    + Explore the correlation between song popularity, artist popularity and other relevant features.
    + Create visualizations (histograms, bar-plots, etc) to visualize the distribution of data(popularity, genre, etc).
3. Implementation of data models based on the statistical methods discussed.
4. Model Interpretation and Visualizations
5. Summarize findings 

