---
title: "STAT605 - Project Proposal"
author: "Group #10"
date: "`r Sys.Date()`"
css: proposal.css
# output: html_document
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra)
```

# Question
Write a one-page proposal (4 points) including code to read data; descriptions of the variables, statistical methods, and computational steps you will use; and a link to your github repository. Turn in a `proposal.html` (knitted from `proposal.Rmd` or from some other source) or a `proposal.pdf`, one per group.


# Code to read the data

Our main data set is located [here](https://media.githubusercontent.com/media/NiharikaCNR/STAT605-Project/main/main_dataset.csv) on GitHub.
```{r, echo=FALSE}
main_data = read_csv("../main_dataset.csv")
```

Our main data set has 26 unique variables as seen below.
```{r}
glimpse(main_data)
```

# Description of Variables

## main_dataset.csv

```{r, echo=FALSE}
description_of_variables = read_csv("description_of_variables.csv")
kable(description_of_variables, format = "html") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed"))
```

# Statistical Methods
```{r}
```

# Computational Steps
```{r}
```
