---
title: "STAT605 - Project Proposal"
author: "Group #10"
date: "`r Sys.Date()`"
css: proposal.css
# output: html_document
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(kableExtra)
```

# Question
Write a one-page proposal (4 points) including code to read data; descriptions of the variables, statistical methods, and computational steps you will use; and a link to your github repository. Turn in a `proposal.html` (knitted from `proposal.Rmd` or from some other source) or a `proposal.pdf`, one per group.


# Code to read the data
```{r}



```

# Description of Variables
<!-- We have multiple connected data sets in out data file. We will be joining and utilizing all of them for our statistical analysis.  -->

<!-- ## artists.csv
1. artist_uri: Artist's URI (in some rare cases can change with time)
2. artist_popularity: Popularity of the artists on a scale of 0 (lowest) - 100 (highest)
3. artist_genres: Genres associated with the artist (generated by Spotify)
4. artist_followers: Number of followers the artist has on Spotify

## final_playlists.csv
1. uri: Playlists' IDs. The contents of playlists may differ drastically from those in the dataset, especially if those playlists have been updated since
2. name: Name of the playlist
3. description: Playlist description
4. query: All of the playlists were found by search in Spotify. From each search roughly 20 playlists were taken. Queries were generated by ChatGPT and are listed in music_genres.txt file.
5. author: Author of the playlist
6. n_tracks: Number of tracks (although for each playlist in this data set only first one hundred of tracks were taken)
7. playlist_followers: Number of followers to the playlist at the time of data collection

## main_dataset.csv
1. track_uri [STRING]: Track's URI
2. name [STRING]: Name of the track
3. artist_names [LIST OF STRINGS]: Names of the artists involved in the song
4. popularity [NUMERIC]: Popularity of the track on a scale of 0 (lowest) - 100 (highest)
5. album_type [STRING]: Format of song release (album, single, or compilation)
6. release_date [DATE]: The date the track was released on
7. artist_uris [LIST OF STRINGS]: URIs of the artists involved
8. playlist_uris [LIST OF STRINGS]: URIs of the playlists the track is in
9. tempo [NUMERIC]: The tempo of the sound track
10. duration_ms [FLOAT]: The duration of the track in milliseconds
11. artists_popularities [LIST OF NUMERIC]: Popularities of the artists involved on a scale of 0 (lowest) - 100 (highest)
12. artist_genres [LIST OF STRINGS]: Genres tagged to each artist involved in the track
13. artists_followers [LIST OF NUMERIC]: Number of followers of each artist involved in the track -->

## main_dataset.csv

```{r, echo=FALSE}
description_of_variables = read_csv("description_of_variables.csv")
kable(description_of_variables, format = "html") %>%
  kable_styling(full_width = F, bootstrap_options = c("condensed"))
```

# Statistical Methods
```{r}
```

# Computational Steps
```{r}
```
