---
title: "STAT605 - Project Proposal"
author: "Group #10"
date: "`r Sys.Date()`"
css: proposal.css
# output: html_document
output: rmdformats::material
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
```

# Project Description

## Problem Statement

+ Providing artist/track popularity analysis to business owners (entertainment label representatives in this case).
+ The analysis could help them market new artists they plan on launching.

## Questions
We are hoping to answer some of these questions through our analysis

__Analysis Questions:__

+ Who is the most popular artist per genre every year? (summary analysis)
+ Top 5 search queries associated with an a track/artist (user input)
+ The top 5 genres of (top 10?) artists on a given year (user input)
+ Is there any correlation between the popularity of an artist and the chances of their songs being included in a playlist for that genre?

__Modeling Questions:__

+ What are the significant factors that influence the popularity of an artist? (Figuring out factors that are statistically significant?)
+ Given a combination of music genres, can we predict the popularity of a track?


# Description of Variables

### Data Source: 
[Kaggle](https://www.kaggle.com/datasets/viktoriiashkurenko/278k-spotify-songs)

### Overview:
The data set being used for the analysis contains information from over 6000 Spotify playlists, with a total of 278,000 songs. The data was collected using __Spotipy__ python library and includes details about artists, playlists and tracks. Besides the basic information (names, popularities and release dates, etc.), there are Spotify-generated audio features such as `danceability`, `energy`, `acousticness` and `speechiness` of each song. The data set also has audio analysis of each song by its URI (Uniform Resource Indicator) information represented as Python dictionaries and are saved in separate pickle files.

### Data files:
The dataset has been divided into 4 different CSV files and two text files.

- artists.csv: contains artist information
- final_playlists.csv: provides details on playlists, including name, author, and number of tracks.
- final_tracks.csv: has individual track details like name, popularity, and release date.
- main_dataset.csv: includes various audio features for each track, such as danceability, energy, and tempo, as well as artist-related information.
- Music_genres.txt: list of types of music on the app.
- im_getting_these_vibes_ul.txt: a text file with tags associated with different songs.

<br>
A sample overview of the data set is in the next section.


# Code to read the data

Our main data set is located [here](https://media.githubusercontent.com/media/NiharikaCNR/STAT605-Project/main/data/main_dataset.csv) on GitHub. It has 26 unique variables as seen below.

```{r, echo=FALSE}
main_data = read_csv("../data/main_dataset.csv")
```

```{r}
glimpse(main_data)
```

# Statistical Methods
```{r}
```

# Computational Steps

1. Data Pre-processing:
    + Handle any missing values in the data set.
    + Remove any duplicate entries.
2. Exploratory Data Analysis:
    + Descriptive Statistics - Generate summary statistics for key variables.
    + Explore the correlation between song popularity, artist popularity and other relevant features.
    + Create visualizations (histograms, bar-plots, etc) to visualize the distribution of data(popularity, genre, etc).
3. Implementation of data models based on the statistical methods discussed.
4. Model Interpretation and Visualizations
5. Summarize findings 

